A secondary screen architecture to accurately capture viewer interactions in interactive TV environments

### 2014-05-01 src/paper.tex
Introduction first version finished

Considering the collective experience of watching TV, the explicit interactions of one viewer can potencialy interfere in the experience of other viewers. Since there is only one remote control and a unique screen (TV screen), explicit interactions that require the use this screen (e.g., evaluate the current content or read viewers comments) end up in an undesired experience for users that are not actively participating of that interactions.

@@

In this scenario, secondary screen devices arise as a powerful mechanism to accurately capture viewer interactions. Other works addressed this separately: identifying viewers~\cite{Cabarcos2011,Hwang2007} and capturing interactions~\cite{Teixeira2010}. In this paper, we present a mechanism that uses

 without interfering in the viewing experience of other people in the TV environment

potential use of mobile devices to capture individual user interactions.

opens up new possibilities to accurately capture individual interactions from TV users. by using secondary screen devices.

>>>>

Considering the collective experience of watching TV, the explicit interactions of one viewer can potentially interfere in the experience of other viewers. Since there is only one remote control and a unique screen (TV screen), explicit interactions that require the use this screen (e.g., evaluate the current content or read viewers comments) end up in an undesired experience for users that are not actively participating of that interactions.

@@

In this scenario, secondary screen devices arise as a powerful mechanism to accurately identify viewers and  capture their interactions. Other works addressed this separately: identifying viewers~\cite{Cabarcos2011,Hwang2007} and capturing interactions~\cite{Teixeira2010}. In this paper, we present an architecture that enables both identifying viewers and capture their interactions. In addition, the architecture described in this paper enables viewers to use the screen of their personal devices to perform explicit interactions without interfering in the experience of the audience in the TV environment.
